Student Log-Data from a Randomized Evaluation of Educational Technology: A Causal Case Study

### 2019-12-17 paper.Rnw
take out regression

matchTEtab <-
  cbind(
    tibble(
      Weights=c('Precision','Precision','ATE','TOT'),
      Regression=c('No','Yes','Yes','Yes')
    ),
    map_dfr(
      effects[c('prec_eff','prec_adj','ate_adj','tot_adj')],
      ~tibble(
        Estimate=unname(.$coefficients),
        "Std. Error"=unname(.$std.error),
        CI=printci(c(.$conf.low,.$conf.high)))
     ),
      `$T_Z$`=NA,
    `$\\rho^2$`=NA
  )

stopifnot(max(matchTEtab[,'Estimate'])<0.25)
stopifnot(min(matchTEtab[,'Estimate'])>0.15)

for(tt in c(ttt['xirt'],ttt['xirt']/2))
  matchTEtab <- add_case(matchTEtab,
    Effect=ifelse(tt==ttt['xirt'],"[Pretest]","[Pretest/2]"),
    Estimate=ancovat[1],
    CI=printci(interval(tt,rrr['xirt'],b=ancovat[1], se=ancovat[2],df=ancova$df)),
    `$\\rho^2$`=rrr['xirt'],
    `$T_Z$`=tt)

matchTEtab <- cbind(
  ` `=c('\\multirow{4}{*}{Estimate}',rep('',3),'\\multirow{2}{*}{Sensitivity}',''),
  matchTEtab
)

matchTEtab <- add_case(matchTEtab,` `='\\hline',.before=5)#,rep(NA,ncol(matchTEtab)-1)),matchTEtab[5:6,])

print(xtable(matchTEtab,
  align='rllrrrrr',
  caption='Estimates with and without regression adjustment and sensitivity analysis of the effect of hint usage.',
  label='tab:matchResults'),
  include.rownames=FALSE,sanitize.text.function =function(x) x)
@

>>>>

matchTEtab <-
  cbind(
    tibble(
      Weights=c('OLS','ATE','TOT'),
#      Regression=c('No','Yes','Yes','Yes')
    ),
    map_dfr(
      c('prec_eff','ate_eff','tot_eff'),
      ~tibble(
        Estimate=unname(effects[[.]]$coefficients),
        "Std. Error"=unname(effects[[.]]$std.error),
        CI=printci(with(effects[[.]],c(conf.low,conf.high))),
        SI1=printci(sens[[.]][1,]),
        SI2=printci(sens[[.]][2,])
      )
    )
  )

##       `$T_Z$`=NA,
##     `$\\rho^2$`=NA
##   )

## stopifnot(max(matchTEtab[,'Estimate'])<0.25)
## stopifnot(min(matchTEtab[,'Estimate'])>0.15)

## for(tt in c(ttt['xirt'],ttt['xirt']/2))
##   matchTEtab <- add_case(matchTEtab,
##     Effect=ifelse(tt==ttt['xirt'],"[Pretest]","[Pretest/2]"),
##     Estimate=ancovat[1],
##     CI=printci(interval(tt,rrr['xirt'],b=ancovat[1], se=ancovat[2],df=ancova$df)),
##     `$\\rho^2$`=rrr['xirt'],
##     `$T_Z$`=tt)

## matchTEtab <- cbind(
##   ` `=c('\\multirow{4}{*}{Estimate}',rep('',3),'\\multirow{2}{*}{Sensitivity}',''),
##   matchTEtab
## )

## matchTEtab <- add_case(matchTEtab,` `='\\hline',.before=5)#,rep(NA,ncol(matchTEtab)-1)),matchTEtab[5:6,])

print(xtable(matchTEtab,
  align='rrllccc',
  caption='Estimates with and without regression adjustment and sensitivity analysis of the effect of hint usage.',
  label='tab:matchResults'),
  include.rownames=FALSE,sanitize.text.function =function(x) x)
@
